Tree Graphs Test

### 2021-07-14 tests/testgraphs.Rmd
Added common names for tree species and information about position

```{r}
y <- tree_diameter1 %>%
  ggplot(aes(x=year, y=diameter, fill=species)) +
  geom_bar(stat='identity', position='dodge', colour="black") +
  coord_flip() +
  scale_x_continuous(limits = c(2010,2015))
y
```

```{r}
z <- tree_diameter1 %>%
  ggplot(aes(x=position, y=diameter, fill=species)) +
  geom_bar(stat="identity", position="dodge") +
  scale_y_continuous(limits = c(0, 60))
z
#order of position - canopy, subcanopy, emergent, sapling 
#consider common names for species 
#add line graph for review
```

@@

>>>>

```{r}
z <- tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", "sapling")) %>%
  ggplot(aes(x=position, y=diameter, fill=species)) +
  geom_bar(stat="identity", position="dodge") +
  scale_y_continuous(limits = c(0, 60))
z
#order of position - canopy, subcanopy, emergent, sapling 
#consider common names for species 
#add line graph for review
```

@@

```{r}
t <- tree_diameter1 %>%
  ggplot(aes(x=year, y=diameter, color=species)) +
  geom_line() + 
  geom_point()
t
```
